Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
tex/VHzQ Section 4 update

We finally focus on SDSS J0959+0227 which is in the VH$z$Q sample from
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
keV rest-frame, so it is an AGN. This object is clearly not a regular
broadline ``Type 1'' AGN, but if with the slightest hint of
variability, this could potentially be a high-$z$ AGN transitioning
from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.

@@

In the North, we assume the UHS J-band depth of 19.6 \citep[Vega; ][]{Dye2018}. 
In the South, one can use the report {\tt ABmagLimits} for each survey in the database, we
can calculate the depths of the various NIR VISTA surveys.
Fig.~\ref{fig:VHS_J_abMagLim} shows this calculated average {\tt AB
MAGLIM} in the VHS.  As one can see, the VHS is not completely
uniform; one area (150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:) has
($Y$, $J$, $H$, $K_{s}$) = (21.1, 20.6, 20.3, 19.8) mag, while a
second area (10$<$RA/deg$<$60, $-60<$Dec$<-40$) has ($Y$, $J$, $H$,
$K_{s}$) = (??, 21.2, 20.6, 20.2) mag.  VIKING is more uniform, with
average depths over the whole VIKING area of ($Z$, $Y$, $J$, $H$,
$K_{s}$) = (22.7, 21.9, 21.4, 21.2, 21.1) mag.

>>>>

We finally focus on SDSS J0959+0227 which is presented in
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
keV rest-frame, so it is an AGN. This object is clearly not a regular
broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
rest-frame UV/very blue, so, so the regular blue QSO continuum could
be emerging Thus, with the slightest hint of variability, this could
potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
2'' object to a broadline Type 1 quasar.

@@

In the North, we assume the UHS J-band depth of 19.6 \citep[Vega;
][]{Dye2018}.  In the South, one can use the report {\tt ABmagLimits}
for each survey in the database, we can calculate the depths of the
various NIR VISTA surveys.  Fig.~\ref{fig:VHS_J_abMagLim} shows this
calculated average {\tt AB MAGLIM} in the VHS.  As one can see, the
VHS is not completely uniform. The area wrapping round
310$\lesssim$RA/deg$\lesssim$90 and -70$\lesssim$ Decl./ deg
$\lesssim$ -40 has a $J$-band depth of 21.2 AB mag, whereas the rest
of the VHS area, the $J$-band depth is closer to 20.6 AB mag.
